Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-08-17 eg6-letters/long-paper/prc-dvcshelium.tex
Start answer AdHoc last paper

To select exclusive events and suppress the backgrounds, we define several 
exclusivity cuts based on energy and momentum conservation. In principle, 
a selection based on two or three variables can be used to guarantee the 
exclusivity of the process. However, in such experiment, where particles 
are detected at very different energies and with very different detector 
resolutions, we chose to over constrain the selection by using seven 
variables. The seven variables are defined as follow for the coherent 
DVCS (replace helium by proton for the incoherent case):
\begin{itemize}
	\item Co-planarity ($\Delta \phi$) of the virtual photon, the real photon and
		the recoil helium, defined as the angle between the helium, virtual photon
		plane and the virtual photon, real photon plane;
	\item Missing energy of the full system;
	\item Missing mass of the full system;
	\item Missing transverse momentum of the full system;
	\item Missing mass of the electron-helium system;
	\item Missing mass of the electron-photon system;
	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
		electron-helium system.
\end{itemize}

@@

The main contamination is expected to be 
from the exclusive production of a $\pi^0$, the final state of which is very similar to DVCS with 
only an extra photon. In such an event, if one of the photons is produced at low energy, it is 
easy to confuse this process with single photon production. In order to estimate the contribution from
this channel in the data, we measure the exclusive $\pi^0$ production in the same way as DVCS, with 
a series of exclusivity cuts, completed by a selection cut on the invariant mass of the two photons
to match the $\pi^0$ mass. The events obtained for the coherent and incoherent
channels are shown in Fig. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}, respectively. From 
this sample, we elaborated an event generator, which after being processed
in the simulation of the detectors gives the red histograms of Fig. \ref{fig:CohPi0Simul} and 
\ref{fig:InCohPi0Simul}. To correct the experimental data, we estimate the number of single photon 
events coming from the exclusive $\pi^0$ production as:
\begin{equation}
	N_{1\gamma,\pi^0}^{Exp} = \frac{N_{1\gamma,\pi^0}^{Sim}}{N_{2\gamma,\pi^0}^{Sim}} \times N_{2\gamma,\pi^0}^{Exp},\\
\end{equation}
where $N_{1\gamma,\pi^0}^{Sim}$ is the number of simulated exclusive $\pi^0$ mistaken for DVCS events,
$N_{2\gamma,\pi^0}^{Sim}$ the number of simulated exclusive $\pi^0$ fully reconstructed and $N_{2\gamma,\pi^0}^{Exp}$
the number of experimentally measured exclusive $\pi^0$. This number can then be subtracted from
the experimentally measured number of DVCS events ($N_{DVCS}^{Exp}$) to get the corrected result: 
\begin{equation}
	N_{DVCS}^{Corr} = N_{DVCS}^{Exp} - N_{1\gamma,\pi^0}^{Exp}.\\
\end{equation}

@@

To evaluate the systematic error of the measurement, we performed several specialized studies. We 
evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
We evaluated the impact of changing the binning in $\phi$ on the extraction of the beam-spin asymmetry
at 90°. The precision with which we know the beam polarization is estimated based on the spread 
of its measurements during the complete run period. We also checked different methods to make the 
simulation of the exclusive $\pi^0$ production to evaluate the 
possible bias introduced by this correction. As radiative corrections are expected to be small
for this process, we did not apply them, but associated an error of their expected value.
These uncertainties are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
evaluated values. They are added quadratically for the total systematic error presented in the results.

@@

Finally, the interference amplitude coefficients are written as:
\begin{equation}
s_{1}^{INT} = F_{A}(t) \Im m(\mathcal{H}_{A}) S_{++}(1),
\end{equation}
with
\begin{eqnarray}
   S_{++}(1) &=& \frac{-8K(2-y)y}{1+\epsilon^2} \left( 1 + 
\frac{1-xA+\frac{\sqrt{1+\epsilon^2}-1}{2}}{1+\epsilon^2} 
\frac{t-t_{min}}{Q^{2}} \right) \label{eq:s1I}
\end{eqnarray}

>>>>

In principle, 
a selection based only on the missing energy of the system would be
enough to guarantee the 
exclusivity of the process. However, in our experiment, where particles 
are detected at very different energies and with very different detector 
resolutions, this method would not be optimal. For instance the momentum 
of the helium nuclei is negligible in the missing energy observable, thus
this valuable information has no impact on a selection using this observable only.
To circumvent this issue, we constrain the selection of our exclusive events by using seven 
variables selected to optimize the use of all the detector information available. 
The seven variables are defined as follow for the coherent 
DVCS (replace helium by proton for the incoherent case):
\begin{itemize}
	\item Co-planarity ($\Delta \phi$) of the virtual photon, the real photon and
		the recoil helium, defined as the angle between the helium, virtual photon
		plane and the virtual photon, real photon plane;
	\item Missing energy of the full system;
	\item Missing mass of the full system;
	\item Missing transverse momentum of the full system;
	\item Missing mass of the electron-helium system;
	\item Missing mass of the electron-photon system;
	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
		electron-helium system.
\end{itemize}

@@

The main contamination is expected to be 
from the exclusive production of a $\pi^0$, the final state of which is very similar to DVCS with 
only an extra photon. In such an event, if one of the photons is produced at low energy, it is 
easy to confuse this process with single photon production. In order to estimate the contribution from
this channel in the data, we measure the exclusive $\pi^0$ production in the same way as DVCS, with 
a series of exclusivity cuts, completed by a selection cut on the invariant mass of the two photons
to match the $\pi^0$ mass. The events obtained for the coherent and incoherent
channels are shown in Fig. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}, respectively. Using 
this sample, we elaborated an event generator by adjusting it to the data after being processed
in the simulation of the detectors. the result of this process is shown with the red histograms 
of Fig. \ref{fig:CohPi0Simul} and 
\ref{fig:InCohPi0Simul}. To correct the experimental data, we estimate the number of single photon 
events coming from the exclusive $\pi^0$ production as:
\begin{equation}
	N_{1\gamma,\pi^0}^{Exp} = \frac{N_{1\gamma,\pi^0}^{Sim}}{N_{2\gamma,\pi^0}^{Sim}} \times N_{2\gamma,\pi^0}^{Exp},\\
\end{equation}
where $N_{1\gamma,\pi^0}^{Sim}$ is the number of simulated exclusive $\pi^0$ mistaken for DVCS events,
$N_{2\gamma,\pi^0}^{Sim}$ the number of simulated exclusive $\pi^0$ fully reconstructed and $N_{2\gamma,\pi^0}^{Exp}$
the number of experimentally measured exclusive $\pi^0$. This number can then be subtracted from
the experimentally measured number of DVCS events ($N_{DVCS}^{Exp}$) to get the corrected result: 
\begin{equation}
	N_{DVCS}^{Corr} = N_{DVCS}^{Exp} - N_{1\gamma,\pi^0}^{Exp}.\\
\end{equation}

@@

To evaluate the systematic error of the measurement, we performed several specialized studies. We 
evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
We evaluated the impact of changing the binning in $\phi$ on the extraction of the beam-spin asymmetry
at 90°. The precision with which we know the beam polarization is estimated based on the spread 
of its measurements during the complete run period. We also checked different methods to make the 
simulation of the exclusive $\pi^0$ production and accounted for a possible undetected 
asymmetry in its signal to evaluate the 
possible bias introduced by this correction. As radiative corrections are expected to be small
for this process, we did not apply them, but associated an error of their expected value.
These uncertainties are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
evaluated values. They are added quadratically for the total systematic error presented in the results.

@@

Finally, the interference amplitude coefficients are written as:
\begin{equation}
s_{1}^{INT} = F_{A}(t) \Im m(\mathcal{H}_{A}) S_{++}(1),
\end{equation}
with
\begin{eqnarray}
   S_{++}(1) &=& \frac{-8K(2-y)y}{1+\epsilon^2} \left( 1 + 
\frac{1-x_A+\frac{\sqrt{1+\epsilon^2}-1}{2}}{1+\epsilon^2} 
\frac{t-t_{min}}{Q^{2}} \right) \label{eq:s1I}
\end{eqnarray}
